Novelty Detection Using Graphical Models for Semantic Room Classification

### 2011-07-04 semantic-nd/article.tex
Disabled colorlinks so it looks nice when printing.
Fixed affliations on article.

% Additional packages
\usepackage[utf8]{inputenc}
\usepackage{subfig}
\usepackage[pdftex,pdfpagelabels,bookmarks,hyperindex,hyperfigures]{hyperref}
\hypersetup{%
   plainpages=false, 
   pdfpagelayout=SinglePage,
   bookmarksopen=false,
   bookmarksnumbered=true,
   breaklinks=true,
   linktocpage,
   colorlinks=true,
   linkcolor=blue,
   urlcolor=blue,
   citecolor=blue,
   anchorcolor=green
}

@@

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
\author{André Susano Pinto\inst{1}\thanks{Email: \email{andresusanopinto@gmail.com}} \and Andrzej Pronobis\inst{2} \and Luis Paulo Reis\inst{1}}
%
%\authorrunning{Lecture Notes in Computer Science: Authors' Instructions}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Faculdade de Engenharia da Universidade do Porto, Portugal,
           \and Royal Institute of Technology, Stockholm, Sweden}

>>>>

% Additional packages
\usepackage[utf8]{inputenc}
\usepackage{subfig}
\usepackage[pdftex,pdfpagelabels,bookmarks,hyperindex,hyperfigures]{hyperref}
\hypersetup{%
   plainpages=false, 
   pdfpagelayout=SinglePage,
   bookmarksopen=false,
   bookmarksnumbered=true,
   breaklinks=true,
   linktocpage,
   colorlinks=true,
   linkcolor=blue,
   urlcolor=blue,
   citecolor=blue,
   anchorcolor=green
}      
\hypersetup{colorlinks=false}

@@

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
\author{André Susano Pinto\inst{1,2} \and Andrzej Pronobis\inst{2} \and Luis Paulo Reis\inst{1,3}}
%
%\authorrunning{Lecture Notes in Computer Science: Authors' Instructions}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Dep.\ Informatics Engineering, Faculty of Engineering of the University of Porto
           \and Centre for Autonomous Systems, The Royal Institute of Technology (KTH)\\
           SE100-44 Stockholm, Sweden
           \and LIACC - Artificial Intelligence And Computer Science Lab.\ - University of Porto \\
           Rua Dr. Roberto Frias, s/n 4200-465 Porto, Portugal}
